---
title: "STA426 EX1PB"
author: "Simon Galkin"
format: 
    html:
        self-contained: true
editor: visual
---

## STA426 EX1PB

> #### Create an executable HTML document with R code that samples 100 values from a log-normal distribution (mu=5, sigma=0.5)

```{r}
set.seed(13)
values <- rlnorm (100, meanlog = 5, sdlog = 0.5)
```

> #### Using the ggplot2 package, create a histogram of the sampled data on both the linear and log scales

1.  (Installing the library)
2.  Importing the library
3.  Plotting histograms

```{r}
#install.packages("ggplot2") 
library("ggplot2")


ggplot(data = data.frame(values), aes(x = values)) +
  geom_histogram(binwidth = 20, color = 'cyan') +
  labs(title = "Linear scale")

ggplot(data = data.frame(values), aes(x = values)) +
  geom_histogram(binwidth = 0.05, color = 'cyan') +
  labs(title = "Log scale") +
  scale_x_log10()
```

> #### Create also a violin plot

```{r}
ggplot(data = data.frame(values), aes(x = values, y = values)) +
  geom_violin(color = 'cyan')

```

> #### Report the mean and standard deviation of your sampled values in line in the text

The mean: `r mean(values)`

The SD: `r sd(values)`

```{r}
#commands that were used to calculate the mean and SD
mean(values)
sd(values)
```
